---
title: "p8105_hw1_mc5296.Rmd"
output: github_document
date: "2022-09-15"
---

# Problem1

## Load the dataset 'penguins'

```{r}
data("penguins", package = "palmerpenguins")
```

## Description of the dataset

```{r}
summary(penguins)
ncol(penguins)
nrow(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

There are penguins' species,island and their bill length, bill depth, flipper length,body mass,sex,and year in the dataset. There are 8 columns and 344 rows,so it is a 344\*8 dataset. The mean of flipper length is 200.9 mm.

## scatter plot

```{r}
library(ggplot2)
ggplot(data = penguins) + geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species))
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

# Problem 2

```{r}
library(tidyverse)
df <- tibble(x1 = rnorm(10),
             vec_logical = (x1>0),
             vec_char = c("a","b","c","d","e","f","g","h","i","j"),
             vec_factor = factor(c("level1","level2","level3","level2","level1","level3","level1","level2","level1","level3"))
             )
df
mean(df$x1)
mean(df$vec_logical)
mean(df$vec_char)
mean(df$vec_factor)
```

The mean function works for random sample, logical vector, character vector and doesn't work for factor vector

## Convert Variable

```{r eval=FALSE}
as.numeric(df$x1)
as.numeric(df$vec_logical)
as.numeric(df$vec_char)
as.numeric(df$vec_factor)
```

The random sample, logical vector and factor vector can be converted to vector while the character vector cannot. This is because elements in random sample are mumerics, logical values can be represented by 0 and 1, factor can be converted to 1, 2, 3, 4... n according to the order in the computer. But character cannot be converted because it is defined as character so it cannot be converted to numeric.
